Covariate Analysis of ROSMAP Reprocessed counts

### 2020-12-16 code/2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38.Rmd
recommit

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = '"syn23640229"';
activityName = 'Covariate Regression';
activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
thisFileName <- '2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

@@

createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38",
                                          parentId ="syn23640229",
                                          folderName = 'RinOver5_RosMap_OldCode')

>>>>

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = '"syn23640229"';
activityName = 'Covariate Regression';
activityDescription = 'Covariate analysis and Regression of aligned effective counts with GRCh38 with CQN normalisation (DLPFC)';
thisFileName <- '2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38.Rmd'
# Github link
thisRepo <- githubr::getRepo(repository = "jgockley62/TWAS", ref="branch", refName='master')
thisFile <- githubr::getPermlink(repository = thisRepo, repositoryPath=paste0('code/',thisFileName))
```

@@

createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_RinEQGt5Cohort_Regress_hg38.Rmd",
                                          parentId ="syn23640229",
                                          folderName = 'RinOver5_RosMap_OldCode')
